MSK IV

### 2017-08-01 msk4-nerve-quiz.rmd
Updated main case and typos in quiz

-  alert{Deep branch of ulnar nerve except lateral 2 lumbricals?}
-  Deep branch of ulnar nerve except medial 2 lumbricals?

@@

-  Median nerve lesion: claw hand
-  alert{Ulnar nerve lesion: claw hand}
-  Diego Maradona: hand of god
-  Ulnar nerve lesion: hand of benediction

>>>>

-  \alert{Deep branch of ulnar nerve except lateral 2 lumbricals?}
-  Deep branch of ulnar nerve except medial 2 lumbricals?

@@

-  Median nerve lesion: claw hand
-  \alert{Ulnar nerve lesion: claw hand}
-  Diego Maradona: hand of god
-  Ulnar nerve lesion: hand of benediction

### 2017-08-01 msk4.rmd
Updated main case and typos in quiz

>>>>

If glenohumeral cause then even passive ROM should be tender.

Natural Hx of RC injury: little evidence for spontaneous repair. Once damaged a bit there is the same amount of force subjected to the same tendon so increased predisposition to further damage.

Natural Hx of RC injury: little evidence for spontaneous repair. Once damaged a bit there is the same amount of force subjected to the same tendon so increased predisposition to further damage.

Natural Hx of RC injury: little evidence for spontaneous repair. Once damaged a bit there is the same amount of force subjected to the same tendon so increased predisposition to further damage.

Risk factors for RC tendinopathy

-  Extrinsic: overhead repeated use, prior injuries, problems in one shoulder can affect the other, anything decreasing ability to heal
-  Intrinsic: shoulder laxity/instability, smoking, Ca, old age

Imaging necessary: not really. Unless red flags, fractures, super old age then don't need to image.

## Trigger 4
